Full title goes here

### 2021-09-18 README.Rmd
Make this more Windows friendly

1. Download and install these fonts:
    - [Cochineal](https://fontesk.com/cochineal-typeface/)
    - [Econ Sans](https://github.com/hrbrmstr/hrbrthemes/tree/master/inst/fonts/econ-sans)
    - [Linux Libertine O](https://www.cufonfonts.com/font/linux-libertine-o) (also [here](https://sourceforge.net/projects/linuxlibertine/))
    - [Libertinus Math](https://github.com/alerque/libertinus)
    - [InconsolataGo](https://github.com/ryanoasis/nerd-fonts/tree/master/patched-fonts/InconsolataGo)
2. [Install R](https://cloud.r-project.org/) (and preferably [RStudio](https://www.rstudio.com/products/rstudio/download/#download)).
    - If you're using macOS, [install XQuartz too](https://www.xquartz.org/), so that you have access to the Cairo graphics library
3. Open `corrupt-caterpillar.Rproj` to open an [RStudio Project](https://r4ds.had.co.nz/workflow-projects.html).
4. Make sure you have a working installation of LaTeX:
    - *Easy-and-recommended way*: Install the [**tinytex** package](https://yihui.org/tinytex/) by running `install.packages("tinytex")` in the R console, then running `tinytex::install_tinytex()`
    - *Easy-but-requires-huge-4+-GB-download way*: Download TeX Live ([macOS](http://www.tug.org/mactex/); [Windows](https://miktex.org/))
5. If it's not installed already, R *should* try to install the **renv** package when you open the RStudio Project for the first time. If you don't see a message about package installation, install it yourself by running `install.packages("renv")` in the R console.
6. Run `renv::restore()` in the R console to install all the required packages for this project.
7. Run `targets::tar_make()` in the R console to automatically download all data files, process the data, run the analysis, and compile the paper and appendix.

>>>>

1. Download and install these fonts:
    - [Cochineal](https://fontesk.com/cochineal-typeface/)
    - [Assistant](https://fonts.google.com/specimen/Assistant)
    - [Linux Libertine O](https://www.cufonfonts.com/font/linux-libertine-o) (also [here](https://sourceforge.net/projects/linuxlibertine/))
    - [Libertinus Math](https://github.com/alerque/libertinus)
    - [InconsolataGo](https://github.com/ryanoasis/nerd-fonts/tree/master/patched-fonts/InconsolataGo)
      - If you're using Windows, make sure you right click on the font files and choose "Install for all users" when installing these fonts
2. [Install R](https://cloud.r-project.org/) (and preferably [RStudio](https://www.rstudio.com/products/rstudio/download/#download)).
    - If you're using macOS, [install XQuartz too](https://www.xquartz.org/) so that you have access to the Cairo graphics library
    - If you're using Windows, [install RTools too](https://cran.r-project.org/bin/windows/Rtools/) and add it to your PATH so that you can install packages from source if needed
3. Open `corrupt-caterpillar.Rproj` to open an [RStudio Project](https://r4ds.had.co.nz/workflow-projects.html).
4. Make sure you have a working installation of LaTeX:
    - *Easy-and-recommended way*: Install the [**tinytex** package](https://yihui.org/tinytex/) by running `install.packages("tinytex")` in the R console, then running `tinytex::install_tinytex()`. The first time you compile a PDF might require an extra minute or so while **tinytex** installs some missing LaTeX packages like csquotes, mathools, and others
    - *Easy-but-requires-huge-4+-GB-download way*: Download TeX Live ([macOS](http://www.tug.org/mactex/); [Windows](https://miktex.org/))
5. If it's not installed already, R *should* try to install the **renv** package when you open the RStudio Project for the first time. If you don't see a message about package installation, install it yourself by running `install.packages("renv")` in the R console.
6. Run `renv::restore()` in the R console to install all the required packages for this project.
7. Run `targets::tar_make()` in the R console to automatically download all data files, process the data, run the analysis, and compile the paper and appendix.

### 2021-09-18 manuscript/manuscript.Rmd
Make this more Windows friendly

---
title: "Full title goes here"
short-title: "Shorter title goes here"
author:
- name: Andrew Heiss
  affiliation: Georgia State University
  email: aheiss@gsu.edu
  url: https://www.andrewheiss.com/
- name: Meng Ye
  affiliation: Georgia State University
  email: mye2@student.gsu.edu
date: "September 18, 2021"
published: Drafting
code-repo: "Access the code at <https://github.com/andrewheiss/corrupt-caterpillar>"
abstract: >-
  Abstract goes here.
keywords: comma, separated, keywords, here
word-count: ""
thanks: >-
  Acknowledgments here if any
reference-section-title: References
bibliography: bibliography.bib
toc: false
title-page: true
endnotes: false
endfloat: false
mainfont: Cochineal
sansfont: Assistant
author-note: >-
  Author note here
correspondence: >-
  Correspondence note here
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: "Full title goes here"
short-title: "Shorter title goes here"
author:
- name: Andrew Heiss
  affiliation: Georgia State University
  email: aheiss@gsu.edu
  url: https://www.andrewheiss.com/
- name: Meng Ye
  affiliation: Georgia State University
  email: mye2@student.gsu.edu
date: "September 18, 2021"
published: Drafting
code-repo: "Access the code at <https://github.com/andrewheiss/corrupt-caterpillar>"
abstract: >-
  Abstract goes here.
keywords: comma, separated, keywords, here
word-count: ""
thanks: >-
  Acknowledgments here if any
reference-section-title: References
bibliography: bibliography.bib
toc: false
title-page: true
endnotes: false
endfloat: false
mainfont: Cochineal
sansfont: Assistant
monofont: '`r if (Sys.info()["sysname"] == "Windows") "InconsolataGo Nerd Font" else "InconsolataGo"`'
ms_mainfont: '`r if (Sys.info()["sysname"] == "Windows") "Linux Libertine" else "Linux Libertine O"`'
ms_sansfont: Assistant
ms_monofont: '`r if (Sys.info()["sysname"] == "Windows") "InconsolataGo Nerd Font" else "InconsolataGo"`'
author-note: >-
  Author note here
correspondence: >-
  Correspondence note here
editor_options: 
  chunk_output_type: console
---
